---
title: "machine_replacement"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Machine Replacement Problem 


# MDP with gaussian rewards

The following script constructs an instance of machien replacement problem as an MDP with guassian reward. 
Find the graph in Figure 1. (Percentile Optimization for Markov Decision Processes with Parameter Uncertainty. Erick Delage, Shie Mannor). Actions: 0 = repair, 1 = not repair. The transition are deterministic. For all state other than last one the repair action cost is independently distributed according to N(130,1). In the last state not-repair action cost is distributed according to N(100,800), while repair is distributed according to N(130,20)


```{r}
num.actions <- 2  # actions: 0 = repair, 1 = not repair
num.states <- 50
discount <- 0.8

mdp.df <-  data.frame(matrix(ncol = 5, nrow = 0))
for (i in seq(1:(num.states-1))){
  idstatefrom <- i
  idstateto  <- i+1
  
  # transitions are deterministic
  probability <- 1
  
  # add a row for repair
  idaction <- 0
  reward <- - rnorm(1, 130,1)
  new.row <- c(idstatefrom,idaction,idstateto,probability,reward)
  mdp.df <- rbind(mdp.df, new.row)
  
  # add a row for not-repair
  idaction <- 1
  reward <- 0
  new.row <- c(idstatefrom,idaction,idstateto,probability,reward)
  mdp.df <- rbind(mdp.df, new.row)
}

# add a row for final state 
  idstatefrom <- num.states
  idstateto  <- num.states
  probability <- 1
  # add a row for repair final state
  idaction <- 0
  reward <- - rnorm(1, 130,20)
  new.row <- c(idstatefrom,idaction,idstateto,probability,reward)
  mdp.df <- rbind(mdp.df, new.row)
  # add a row for not-repair final state
  idaction <- 1
  reward <- - rnorm(1, 100,800)
  new.row <- c(idstatefrom,idaction,idstateto,probability,reward)
  mdp.df <- rbind(mdp.df, new.row)
  
  
colnames(mdp.df) <- c("idstatefrom","idaction","idstateto","probability","reward")

print(mdp.df)
write.csv(mdp.df,"machine_replacement_mdp.csv", row.names = FALSE)
```

# MDP with Dirichlet Prior on Transition
The following scripts genereate an instance of machine replacement problem MDP with 10 states, 2 actions, a discount factor of 0.8. Find the graph in Figure 3. (Percentile Optimization for Markov Decision Processes with Parameter Uncertainty. Erick Delage, Shie Mannor). States 1 to 8 describe the normal aging machine, while states R1 (id=10) and R2 (id=9) repesent two possible stages of repairs: R1 for normal repairs on machine costing 2, and R2 for harder one with a harder one with a cost of 10.  Letting the machine reach the age of 8 is penalized with a cost of 20. 

```{r}
num.actions <- 2  # actions: 0 = repair, 1 = not repair
num.states <- 10
discount <- 0.8

mdp.df <-  data.frame(matrix(ncol = 5, nrow = 0))

for (i in seq(1:7)){
  # rows idstatefrom,idaction,idstateto,probability,reward
  # action 0 = do nothin 
  mdp.df <- rbind(mdp.df, c(i,0,i,0.2,0))
  mdp.df <- rbind(mdp.df, c(i,0,i+1,0.8,0))
  # action 1 = repair  
  mdp.df <- rbind(mdp.df, c(i,1,i+1,0.3,0))
  # R1 - cost 2
  mdp.df <- rbind(mdp.df, c(i,1,10,0.6,-2))
  # R2 - cost 10
  mdp.df <- rbind(mdp.df, c(i,1,9,0.1,-10))
}

colnames(mdp.df) <- c("idstatefrom","idaction","idstateto","probability","reward")

# State 8
mdp.df <- rbind(mdp.df, c(8,0,8,1,-20))
mdp.df <- rbind(mdp.df, c(8,1,8,0.3,-20))
mdp.df <- rbind(mdp.df, c(8,1,10,0.6,-2))
mdp.df <- rbind(mdp.df, c(8,1,9,0.1,-10))

# Reachin 8 cost 20
mdp.df$reward[mdp.df$idstateto == 8] <- -20

#state R1 
mdp.df <- rbind(mdp.df, c(10,0,10,0.2,-2))
mdp.df <- rbind(mdp.df, c(10,0,1,0.8,0))
mdp.df <- rbind(mdp.df, c(10,1,10,1,-2))


#S tate R2
mdp.df <- rbind(mdp.df, c(9,0,9,1,-10))
mdp.df <- rbind(mdp.df, c(9,1,10,0.6,-2))
mdp.df <- rbind(mdp.df, c(9,1,9,0.4,-10))


print(mdp.df)
write.csv(mdp.df,"machine_replacement_mdp.csv", row.names = FALSE)
```

